---
title: State Of Organic Seed Data
resource_files:
- www/cropped-logo-header.png
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    source_code: embed
    storyboard: true
    orientation: columns
    vertical_layout: fill
    logo: www/logo.png
    theme: 
      version: 4
      #bg: "#90A7B1"
      #fg: "#D3D3D3" 
      #primary: "#D3D3D3"
      navbar-bg: "#4E7C8F"
      base_font: Hind
        #google: Prompt
      heading_font:
        google: Hind
      code_font:
        google: 
          # arguments to sass::font_google() 
          family: JetBrains Mono
          local: false
---

```{css, echo=FALSE}
h1{font-size:18px;}
h2{font-size:16px;}
.title {
  background-color: #2d677f;
  color:#ffffff;
  padding-right: 200px;
  padding-top: 10px;
  padding-left: 10px;
  padding-bottom: 10px;
}

.box {
  padding: 1em;
  background: white;
  border: 2px solid black;
  border-radius: 10px;
}

.storyboard-nav .sbframelist .li {
  background: #90A7B1
  font-size: 16px;
}

```

<script>
var navbar = $('#navbar');
        navbar.on("click", "a[data-toggle!=dropdown]", null, function () {
//           alert($(this).attr('href'));
           Shiny.setInputValue("active_tab", $(this).attr('href'));
        });
</script>

```{r message=FALSE, warning=FALSE, include=FALSE, cache=TRUE, context="setup"}

# install packages and prep data
source("setup.R")
source("setup_liza.R")

# custom graph functions
source("functions.R")
source("functions_researcher.R")
source("functions_seedproducer.R")
source("functions_network.R")

# Set default font to Hind. It wasn't working when I put this in the setup file...
font_add_google(name = "Hind", family = "Hind")
showtext_auto()

```


Filter {.sidebar data-width=300}
=====================================
```{r}

renderUI({
   sel <- input$active_tab

   if (is.null(sel) || sel == "#section-introduction") {
    tagList(
      tags$br(""),
      tags$p("For most of this site, this sidebar will contain menus and buttons that will allow you to filter through the data and adjust the appearance of the figures")
      
      )} else if  (sel == "#section-farm-demographics"
                    || sel == "#section-producer-types"
                    || sel == "#section-organic-vegetable-seed-usage"
                    || sel == "#section-organic-cover-crop-seed-usage"
                    || sel == "#section-organic-field-crop-seed-usage" 
                    || sel == "#section-organic-forage-crop-seed-usage"             
                    || sel == "#section-organic-seed-usage"
                    || sel == "#change-in-organic-seed-usage" 
                    || sel == "#section-seed-sources"
                    || sel == "#section-certifier-involvement-with-organic-seed-use"
                    || sel == "#section-organic-seed-production"
                    || sel == "#section-factors-in-not-purchasing-organic-seed"
                    || sel == "#section-opinions-on-genetic-engineering-and-organic-seeds"
                    || sel == "#section-organic-breeding-needs") {
    tagList(
      
      selectInput("state", "State:", choices=c("All",sort(unique(data$state))), 
                  selected="All", multiple=TRUE),
      checkboxInput("Y2021", "Display 2021 Data", TRUE),
      checkboxInput("Y2016", "Display 2016 Data", TRUE),
      checkboxInput("Y2011", "Display 2011 Data", TRUE),
      radioButtons("crop_type", "Crop Types Grown:",
                 c("All" = "all",
                   "Vegetables and Other Crops" = "has_veg",
                   "Only Vegetables" = "only_veg",
                   "Field Crops and Other Crops" = "has_field",
                   "Only Field Crops" = "only_field",
                   "Forage Crops and Other Crops" = "has_forage",
                   "Only Forage Crops" = "only_forage")),
      
      selectInput("crop_size", "Farm Size (Acres):", choices=c(
                  "All",
                  "0.01 - 3",
                  "3.01 - 10",
                  "10.01 - 50",
                  "50.01 - 80",
                  "80.01 - 160",
                  "160.01 - 480",
                  ">480"), selected="All", multiple=TRUE),
      
      checkboxInput("show_n", "Display response numbers", FALSE),
      checkboxInput("show_title", "Display title in figure", TRUE),
  
      radioButtons("color_palette", "Color Palette:",
                 c("Default" = "default",
                   "Colorblind friendly" = "colorblind",
                   "Grayscale" = "grayscale"))
      
    )} else if  (sel == "#section-additional-figures") {
    tagList(
      
      checkboxInput("show_title", "Display title in figure", TRUE),
  
      radioButtons("color_palette", "Color Palette:",
                 c("Default" = "default",
                   "Colorblind friendly" = "colorblind",
                   "Grayscale" = "grayscale"))
      
    )} else if ( sel == "#section-seed-producer-demographics"
                    #|| sel == "#section-operation-details"
                    || sel == "#section-challenges"
                    || sel == "#section-seed-producer-perspectives") {
    tagList(
      selectInput("region_p", "Region:", 
           choices=c("All",sort(unique(df.p.slim$Region))[-c(1,3)]), 
           selected="All", multiple=F),

      selectInput("activity_p", "Seed-related activities:", 
            choices=c("All",
                      "Seed breeding & production only" = "Producer only",
                      "Seed production & retail" = "Producer & Retailer"),
            selected="All", multiple=F),

            selectInput("crop_type_p", "Crop types:", choices=c("All",
                                                  "Vegetables" = "cropcat_veg",
                                                  "Ornamentals" = "cropcat_orn",
                                                  "Grains" = "cropcat_grain",
                                                  "Potato/prop." = "cropcat_propogules",
                                                  "Field" = "cropcat_field",
                                                  "Forage" = "cropcat_forage",
                                                  "Herbs" = "cropcat_herbs"), 
            selected="All", multiple=F),

      radioButtons("color_palette_p", "Color Palette:",
                 c("Default" = "default",
                   "Colorblind friendly" = "colorblind",
                   "Grayscale" = "grayscale"))
    )} else if (sel == "#section-researcher-demographics"
                    #|| sel == "#section-researcher-profile"
                    || sel == "#section-project-outcomes"
                    || sel == "#section-researcher-perspectives") {
    tagList(
      selectInput("region_r", "Region:", 
           choices=c("All",sort(unique(df.r$Region))[-c(1)]), 
           selected="All", multiple=F),

      selectInput("crop_type_r", "Crop types:", 
                  choices=c("All", unique(c(df.r.long$crop_type))), 
            selected="All", multiple=F),
      
      radioButtons("color_palette_r", "Color Palette:",
                 c("Default" = "default",
                   "Colorblind friendly" = "colorblind",
                   "Grayscale" = "grayscale"))
    )} else if ( #|| sel == "#section-network-data-collection"
                    sel == "#section-seed-network") {
    tagList(
      selectInput("region_n", "Region:", 
            choices=c("All",sort(unique(nodes$Region))[-c(1,3,6)]), 
            selected="All", multiple=F),

      selectInput("net_type", "Connection type:", 
            choices=c("All",
                      "Information & research" = "education",
                      "Supply chain connections" = "operation",
                      "Genetic material movement" = "genetic"),
            selected="All", multiple=F)
      
    )} else {
     
    }
})
```

Introduction {data-navmenu="Crop producers"  data-width=700}
=====================================

### Welcome

<b>Welcome to the State Of Organic Seed Producer Survey interactive report.</b>

State of Organic Seed is a project of Organic Seed Alliance that monitors the status of organic seed in the US and provides a roadmap for increasing the diversity, quality, and integrity of organic seed available.

In 2021, we conducted a national survey of certified organic crop growers to assess their attitudes and perceptions regarding organic seed, their current use of organic seed, and any obstacles that restrict organic seed sourcing. The survey also asked which crops and traits should be prioritized through organic plant breeding programs. Many additional topics were covered in this survey. We conducted a survey in 2011 and 2016 that asked many of the same questions, allowing us to measure our progress over the last five and ten years. 

This interactive report presents, in graphical form, the results of the latest organic farmer survey. It allow you to look at the responses from all farmers, or to view the responses from specific states. 

This survey was conducted in conjunction with the Organic Farming Research Foundation with funding by the USDA Organic Research and Education Initiative.

Farm Demographics {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================

### Farm Locations

```{r}
plotOutput("Map")
```

```{r, context="server", Map,  echo=FALSE}
output$Map <- renderPlot({
      
      MapPlot (input = input)
      
    })  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Farm Regions

```{r}
plotOutput("Regions")
```

```{r, context="server", Regions,  echo=FALSE}
output$Regions <- renderPlot({
    GradientMap (input = input, question = "RegionTotal", title = "Regions", catlab =  "Number of Respondents", year = "2021")
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)


```

### Year Certified 

```{r}
plotOutput("Years")
```

```{r, context="server", Years, echo=FALSE}
output$Years <-  renderPlot({
  
BinPlot (input = input, question = "YearsCertified_bin", title = "Years Certified", xlab = XLabel(input,"Years certified"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

Producer Types {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================

### Vegetable Producer 

```{r}
plotOutput("VegProducer")
```

```{r, context="server", VegProducer, echo=FALSE}
output$VegProducer <- renderPlot({
  
BoxPlot (input = input, question = "GrowVegis", title = "Percentage of Respondents who Produce Vegetables", xlab = "", ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Vegetable Acreage

```{r}
plotOutput("VegAcre")
```

```{r, context="server", VegAcre, echo=FALSE}
output$VegAcre <- renderPlot({
  
BinPlot (input = input, question = "VegiAcreageBins", title = "Vegetable Acreage", xlab = XLabel(input,"Vegetable acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Cover Crop Producer

```{r}
plotOutput("CoverProducer")
```

```{r, context="server", CoverProducer, echo=FALSE}
output$CoverProducer <- renderPlot({
  
BoxPlot (input = input, question = "GrowCover", title = "Percentage of Respondents who Produce Cover Crops or Green Pasture", xlab = "", ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Cover Crop Acreage

```{r}
plotOutput("CoverAcre")
```

```{r, context="server", CoverAcre, echo=FALSE}
output$CoverAcre <- renderPlot({
  
BinPlot (input = input, question = "CoverAcreageBins", title = "Cover Crop Acreage", xlab = XLabel(input, "Cover crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Field Crop Producer

```{r}
plotOutput("FieldProducer")
```

```{r, context="server", FieldProducer, echo=FALSE}
output$FieldProducer <-  renderPlot({
  
BoxPlot (input = input, question = "GrowField", title = "Percentage of Respondents who Produce Field Crops", xlab = "", ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Field Crop Acreage

```{r}
plotOutput("FieldAcre")
```

```{r, context="server", FieldAcre, echo=FALSE}
output$FieldAcre <- renderPlot({
  
BinPlot (input = input, question = "FieldAcreageBins", title = "Field Crop Acreage", xlab = XLabel(input,"Field crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Forage Crop Producer

```{r}
plotOutput("ForageProducer")
```

```{r, context="server", ForageProducer, echo=FALSE}
output$ForageProducer <- renderPlot({
  
BoxPlot (input = input, question = "GrowForage", title = "Percentage of Respondents who Produce Forage Crops", xlab = "", ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Forage Crop Acreage

```{r}
plotOutput("ForageAcre")
```

```{r, context="server", ForageAcre, echo=FALSE}
output$ForageAcre <- renderPlot({
  
BinPlot (input = input, question = "ForageAcreageBins", title = "Forage Crop Acreage", xlab = XLabel(input,"Forage crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

Organic Vegetable Seed Usage {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================
  
### Overall Vegetable Seed Use
  
```{r}
plotOutput("VegOGSeed")
```

```{r, context="server", VegOGSeed, echo=FALSE}
output$VegOGSeed <- renderPlot({
  
BoxPlot (input = input, question = "OGVegiSeed", title = "Percent Vegetable Acreage Planted To Organic Seed", xlab = XLabel(input,"Vegetable acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Range of Vegetable Seed Use

```{r}
plotOutput("OGVegiSeedBins")
```

```{r, context="server", OGVegiSeedBins, echo=FALSE}
output$OGVegiSeedBins <- renderPlot({
  
  BinPlot (input = input, question = "OGVegiSeedBins", title = "Percent Vegetable Acreage Planted To Organic Seed", xlab = XLabel(input, "Percentage of vegetable acreage planted to organic seed"), ylab = "Percentage of repondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Vegetable Seed Use by Vegetable Acreage
  
```{r}
plotOutput("VegOGSeedByAcreage")
```

```{r, context="server", VegOGSeedByAcreage, echo=FALSE}
output$VegOGSeedByAcreage <- renderPlot({
  
CatPlot (input = input, category = "VegiAcreageBins", question = "OGVegiSeed", title = "Percent Vegetable Acreage Planted To Organic Seed", xlab = XLabel(input,"Vegetable acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Map of 2021 Vegetable Seed Use

```{r}
# Need to figure out how to hide the chunks if the map is not displayed
plotOutput("OGVegiSeedMap2021")
```

```{r, context="server", OGVegiSeedMap2021, echo=FALSE}

output$OGVegiSeedMap2021 <- renderPlot({
  if (input$Y2021 & input$state == "All") {
    GradientMap (input = input, question = "OGVegiSeed", title = "2021 Percent Vegetable Acreage Planted To Organic Seed", catlab =  "Percentage", year = "2021")
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Map of 2016 Vegetable Seed Use

```{r}
plotOutput("OGVegiSeedMap2016")
```

```{r, context="server", OGVegiSeedMap2016, echo=FALSE}

output$OGVegiSeedMap2016 <- renderPlot({
  if (input$Y2016 & input$state == "All") {
    GradientMap (input = input, question = "OGVegiSeed", title = "2016 Percent Vegetable Acreage Planted To Organic Seed", catlab =  "Percentage", year = "2016")
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Map of 2011 Vegetable Seed Use

```{r}
plotOutput("OGVegiSeedMap2011")
```

```{r, context="server", OGVegiSeedMap2011, echo=FALSE}
output$OGVegiSeedMap2011 <- renderPlot({
  if (input$Y2011 & input$state == "All") {
    GradientMap (input = input, question = "OGVegiSeed", title = "2011 Percent Vegetable Acreage Planted To Organic Seed", catlab =  "Percentage", year = "2011")
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

Organic Cover Crop Seed Usage {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================

### Cover Crop Seed Use

```{r}
plotOutput("CoverOGSeed")
```

```{r, context="server", CoverOGSeed, echo=FALSE}
output$CoverOGSeed <- renderPlot({
  BoxPlot (input = input, question = "OGCoverSeed", title = "Percent Cover Crop Acreage Planted To Organic Seed", xlab = XLabel(input, "Cover crop acreage"), ylab = "Percentage")
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Range of Cover Crop Seed Use

```{r}
plotOutput("OGCoverSeedBins")
```

```{r, context="server", OGCoverSeedBins, echo=FALSE}
output$OGCoverSeedBins <- renderPlot({
  
  BinPlot (input = input, question = "OGCoverSeedBins", title = "Percent Cover Crop Acreage Planted To Organic Seed", xlab = XLabel(input,"Percentage of cover crop acreage planted to organic seed"), ylab = "Percentage of repondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Cover Crop Seed Use by Cover Crop Acreage
  
```{r}
plotOutput("CoverOGSeedByAcreage")
```

```{r, context="server", CoverOGSeedByAcreage, echo=FALSE}
output$CoverOGSeedByAcreage <- renderPlot({
  
CatPlot (input = input, category = "CoverAcreageBins", question = "OGCoverSeed", title = "Percent Cover Crop Acreage Planted To Organic Seed", xlab = XLabel(input,"Cover crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Map of 2021 Cover Crop Seed Use

```{r}
plotOutput("OGCoverSeedMap2021")
```

```{r, context="server", OGCoverSeedMap2021, echo=FALSE}

output$OGCoverSeedMap2021 <- renderPlot({
  if (input$Y2021 & input$state == "All") {
    GradientMap (input = input, question = "OGCoverSeed", title = "2021 Percent Cover Crop Acreage Planted To Organic Seed", catlab =  "Percentage", year = "2021")
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Map of 2016 Cover Crop Seed Use

```{r}
plotOutput("OGCoverSeedMap2016")
```

```{r, context="server", OGCoverSeedMap2016, echo=FALSE}

output$OGCoverSeedMap2016 <- renderPlot({
  if (input$Y2016 & input$state == "All") {
    GradientMap (input = input, question = "OGCoverSeed", title = "2016 Percent Cover Crop Acreage Planted To Organic Seed", catlab =  "Percentage", year = "2016")
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

Organic Field Crop Seed Usage {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================

### Overall Field Crop Seed Use
  
```{r}
plotOutput("FieldOGSeed")
```

```{r, context="server", FieldOGSeed, echo=FALSE}
output$FieldOGSeed <- renderPlot({
  
BoxPlot (input = input, question = "OGFieldSeed", title = "Percent Field Crop Acreage Planted To Organic Seed", xlab = XLabel(input,"Field crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Range of Field Crop Seed Use

```{r}
plotOutput("OGFieldSeedBins")
```

```{r, context="server", OGFieldSeedBins, echo=FALSE}
output$OGFieldSeedBins <- renderPlot({
  
  BinPlot (input = input, question = "OGFieldSeedBins", title = "Percent Field Crop Acreage Planted To Organic Seed", xlab = XLabel(input,"Percentage of field crop acreage planted to organic seed"), ylab = "Percentage of repondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Field Crop Seed Use by Field Crop Acreage
  
```{r}
plotOutput("FieldOGSeedByAcreage")
```

```{r, context="server", FieldOGSeedByAcreage, echo=FALSE}
output$FieldOGSeedByAcreage <- renderPlot({
  
CatPlot (input = input, category = "FieldAcreageBins", question = "OGFieldSeed", title = "Percent Field Crop Acreage Planted To Organic Seed", xlab = XLabel(input,"Field crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Map of 2021 Field Crop Seed Use

```{r}
# Need to figure out how to hide the chunks if the map is not displayed
plotOutput("OGFieldSeedMap2021")
```

```{r, context="server", OGFieldSeedMap2021, echo=FALSE}

output$OGFieldSeedMap2021 <- renderPlot({
  if (input$Y2021 & input$state == "All") {
    GradientMap (input = input, question = "OGFieldSeed", title = "2021 Percent Field Crop Acreage Planted To Organic Seed", catlab =  "Percentage", year = "2021")
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Map of 2016 Field Crop Seed Use

```{r}
plotOutput("OGFieldSeedMap2016")
```

```{r, context="server", OGFieldSeedMap2016, echo=FALSE}

output$OGFieldSeedMap2016 <- renderPlot({
  if (input$Y2016 & input$state == "All") {
    GradientMap (input = input, question = "OGFieldSeed", title = "2016 Percent Field Crop Acreage Planted To Organic Seed", catlab =  "Percentage", year = "2016")
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Map of 2011 Field Crop Seed Use

```{r}
plotOutput("OGFieldSeedMap2011")
```

```{r, context="server", OGFieldSeedMap2011, echo=FALSE}
output$OGFieldSeedMap2011 <- renderPlot({
  if (input$Y2011 & input$state == "All") {
    GradientMap (input = input, question = "OGFieldSeed", title = "2011 Percent Field Crop Acreage Planted To Organic Seed", catlab =  "Percentage", year = "2011")
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

Organic Forage Crop Seed Usage {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================

### Overall Forage Crop Seed Use
  
```{r}
plotOutput("ForageOGSeed")
```

```{r, context="server", ForageOGSeed, echo=FALSE}
output$ForageOGSeed <- renderPlot({
  
BoxPlot (input = input, question = "OGForageSeed", title = "Percent Forage Crop Acreage Planted To Organic Seed", xlab = XLabel(input, "Forage crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Range of Forage Crop Seed Use

```{r}
plotOutput("OGForageSeedBins")
```

```{r, context="server", OGForageSeedBins, echo=FALSE}
output$OGForageSeedBins <- renderPlot({
  
  BinPlot (input = input, question = "OGForageSeedBins", title = "Percent Forage Crop Acreage Planted To Organic Seed", xlab = XLabel(input, "Percentage of forage crop acreage planted to organic seed"), ylab = "Percentage of repondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Forage Crop Seed Use by Forage Crop Acreage
  
```{r}
plotOutput("ForageOGSeedByAcreage")
```

```{r, context="server", ForageOGSeedByAcreage, echo=FALSE}
output$ForageOGSeedByAcreage <- renderPlot({
  
CatPlot (input = input, category = "ForageAcreageBins", question = "OGForageSeed", title = "Percent Forage Crop Acreage Planted To Organic Seed", xlab = XLabel(input,"Forage crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Map of 2021 Forage Crop Seed Use

```{r}
# Need to figure out how to hide the chunks if the map is not displayed
plotOutput("OGForageSeedMap2021")
```

```{r, context="server", OGForageSeedMap2021, echo=FALSE}

output$OGForageSeedMap2021 <- renderPlot({
  if (input$Y2021 & input$state == "All") {
    GradientMap (input = input, question = "OGForageSeed", title = "2021 Percent Forage Crop Acreage Planted To Organic Seed", catlab =  "Percentage", year = "2021")
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Map of 2016 Forage Crop Seed Use

```{r}
plotOutput("OGForageSeedMap2016")
```

```{r, context="server", OGForageSeedMap2016, echo=FALSE}

output$OGForageSeedMap2016 <- renderPlot({
  if (input$Y2016 & input$state == "All") {
    GradientMap (input = input, question = "OGForageSeed", title = "2016 Percent Forage Crop Acreage Planted To Organic Seed", catlab =  "Percentage", year = "2016")
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Map of 2011 Forage Crop Seed Use

```{r}
plotOutput("OGForageSeedMap2011")
```

```{r, context="server", OGForageSeedMap2011, echo=FALSE}
output$OGForageSeedMap2011 <- renderPlot({
  if (input$Y2011 & input$state == "All") {
    GradientMap (input = input, question = "OGForageSeed", title = "2011 Percent Forage Crop Acreage Planted To Organic Seed", catlab =  "Percentage", year = "2011")
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

100% Organic Seed Usage {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================

### Using All Organic Seed

```{r}
plotOutput("AllOGSeed")
```

```{r, context="server", AllOGSeed, echo=FALSE}
output$AllOGSeed <- renderPlot({
  
  BoxPlot (input = input, question = "AllOGSeed", title = "Percentage of Producers Using Only Organic Seed", xlab = XLabel(input,"Share of producers"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### 100% Organic Seed Usage by Total Crop Acreage
  
```{r}
plotOutput("AllOGSeedByAcreage")
```

```{r, context="server", AllOGSeedByAcreage, echo=FALSE}
output$AllOGSeedByAcreage <- renderPlot({
  
CatPlot (input = input, category = "TotalAcreageBins", question = "AllOGSeed", title = "Percentage of Producers Using Only Organic Seed", xlab = XLabel(input,"Total crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### 2021 Regional Map of All Organic Seed Use

```{r}
plotOutput("AllOGSeed2021Map")
```

```{r, context="server", AllOGSeed2021Map, echo=FALSE}
output$AllOGSeed2021Map <- renderPlot({
  if (input$Y2021 & input$state == "All") {
    
    GradientMap (input = input, question = "AllOGSeed", title = "Percentage of 2021 Producers Using Only Organic Seed", catlab =  "Percentage", year = "2021")
    
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### 2016 Regional Map of All Organic Seed Use

```{r}
plotOutput("AllOGSeed2016Map")
```

```{r, context="server", AllOGSeed2016Map, echo=FALSE}
output$AllOGSeed2016Map <- renderPlot({
  if (input$Y2016 & input$state == "All") {
    
    GradientMap (input = input, question = "AllOGSeed", title = "Percentage of 2016 Producers Using Only Organic Seed", catlab =  "Percentage", year = "2016")
    
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### 2011 Regional Map of All Organic Seed Use

```{r}
plotOutput("AllOGSeed2011Map")
```

```{r, context="server", AllOGSeed2011Map, echo=FALSE}
output$AllOGSeed2011Map <- renderPlot({
  if (input$Y2011 & input$state == "All") {
    
    GradientMap (input = input, question = "AllOGSeed", title = "Percentage of 2011 Producers Using Only Organic Seed", catlab =  "Percentage", year = "2011")
    
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

Change in Organic Seed Usage {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================

### Change in Organic Vegetable Seed Usage

```{r}
plotOutput("IncreasedOGVegSeed")
```

```{r, context="server", IncreasedOGVegSeed, echo=FALSE}
output$IncreasedOGVegSeed <- renderPlot({
  
  BinPlot (input = input, question = "IncreasedOGVegSeed", title = "Over the last 3 years, have you decreased or increased the percentage of organic seed that you use in vegetable crops", xlab = XLabel(input, "Organic seed usage change"), ylab = "Percentage of Respondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Change in Organic Field Crop Seed Usage

```{r}
plotOutput("IncreasedOGFieldSeed")
```

```{r, context="server", IncreasedOGFieldSeed, echo=FALSE}
output$IncreasedOGFieldSeed <- renderPlot({
  
  BinPlot (input = input, question = "IncreasedOGFieldSeed", title = "Over the last 3 years, have you decreased or increased the percentage of organic seed that you use in field crops", xlab = XLabel(input, "Organic seed usage change"), ylab = "Percentage of Respondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Change in Organic Cover Crop Seed Usage

```{r}
plotOutput("IncreasedOGCoverSeed")
```

```{r, context="server", IncreasedOGCoverSeed, echo=FALSE}
output$IncreasedOGCoverSeed <- renderPlot({
  
  BinPlot (input = input, question = "IncreasedOGCoverSeed", title = "Over the last 3 years, have you decreased or increased the percentage of organic seed that you use in cover crops", xlab = XLabel(input, "Organic seed usage change"), ylab = "Percentage of Respondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Change in Organic Forage Crop Seed Usage

```{r}
plotOutput("IncreasedOGForageSeed")
```

```{r, context="server", IncreasedOGForageSeed, echo=FALSE}
output$IncreasedOGForageSeed <- renderPlot({
  
  BinPlot (input = input, question = "IncreasedOGForageSeed", title = "Over the last 3 years, have you decreased or increased the percentage of organic seed that you use in forage crops", xlab = XLabel(input, "Organic seed usage change"), ylab = "Percentage of Respondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

Seed Sources {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================
  
### Seed Sourced From Own Production
  
```{r}
plotOutput("SeedSourceOwn")
```

```{r, context="server", SeedSourceOwn, echo=FALSE}
output$SeedSourceOwn <- renderPlot({
  
  BoxPlot (input = input, question = "SeedSourceOwn", title = "Average Percentage of Seed Used That Was Sourced From Own Production", xlab = XLabel(input, "Average amount sourced"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Seed Sourced From Processor or Buyer

```{r}
plotOutput("SeedSourceBuyer")
```

```{r, context="server", SeedSourceBuyer, echo=FALSE}
output$SeedSourceBuyer <- renderPlot({
  
  BoxPlot (input = input, question = "SeedSourceBuyer", title = "Average Percentage of Seed Used That Was Sourced From Processor or Buyer", xlab = XLabel(input, "Average amount sourced"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Seed Sourced Directly From Seed Company

```{r}
plotOutput("SeedSourceComp")
```

```{r, context="server", SeedSourceComp, echo=FALSE}
output$SeedSourceComp <- renderPlot({
  
  BoxPlot (input = input, question = "SeedSourceComp", title = "Average Percentage of Seed Used That Was Sourced Directly From Seed Company (via catalog, sales rep, etc)", xlab = XLabel(input, "Average amount sourced"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Seed Sourced Directly From Farm or Garden Store

```{r}
plotOutput("SeedSourceGardenCenter")
```

```{r, context="server", SeedSourceGardenCenter, echo=FALSE}
output$SeedSourceGardenCenter <- renderPlot({
  
  BoxPlot (input = input, question = "SeedSourceGardenCenter", title = "Average Percentage of Seed Used That Was Sourced From Farm or Garden Store", xlab = XLabel(input, "Average amount sourced"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Seed Sourced Directly From Other Farmers
```{r}
plotOutput("SeedSourceFarm")
```

```{r, context="server", SeedSourceFarm, echo=FALSE}
output$SeedSourceFarm <- renderPlot({
  
  BoxPlot (input = input, question = "SeedSourceFarm", title = "Average Percentage of Seed Used That Was Sourced From Other Farmers", xlab = XLabel(input, "Average amount sourced"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

Certifier Involvement with Organic Seed Use {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================
  
### Certifier Requests Greater Steps for Organic Seed
  
```{r}
plotOutput("CertifierRequest")
```

```{r, context="server", CertifierRequest, echo=FALSE}
output$CertifierRequest <- renderPlot({
  
  BinPlot (input = input, question = "CertifierRequest", title = "Over the last 3 years, has your certifier requested that you take greater steps to source organic seed?", xlab = XLabel(input, "Response"), ylab = "Percentage of Respondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Certifier Requests Trials of Available Organic Varieties

```{r}
plotOutput("AddStepsTrial")
```

```{r, context="server", AddStepsTrial, echo=FALSE}
output$AddStepsTrial <- renderPlot({
  
  BinPlot (input = input, question = "AddStepsTrial", title = "If your certifier requested additional steps to source organic seed, did they ask that you conduct trials of available organic varieties?", xlab = XLabel(input, "Response"), ylab = "Percentage of Respondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Certifier Requests Searching Online Database

```{r}
plotOutput("AddStepsSeedFinder")
```

```{r, context="server", AddStepsSeedFinder, echo=FALSE}
output$AddStepsSeedFinder <- renderPlot({
  
  BinPlot (input = input, question = "AddStepsSeedFinder", title = "If your certifier requested additional steps to source organic seed, did they ask that you search Organic Seed Finder or another online database?", xlab = XLabel(input, "Response"), ylab = "Percentage of Respondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Certifier Requests Researching More Than 3 Seed Catalogs

```{r}
plotOutput("AddStepsCat")
```

```{r, context="server", AddStepsCat, echo=FALSE}
output$AddStepsCat <- renderPlot({
  
  BinPlot (input = input, question = "AddStepsCat", title = "If your certifier requested additional steps to source organic seed, did they ask that you research more than 3 seed catalogs?", xlab = XLabel(input, "Response"), ylab = "Percentage of Respondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Certifier Requests Requesting Seed in a Timely Manner

```{r}
plotOutput("AddStepsTimely")
```

```{r, context="server", AddStepsTimely, echo=FALSE}
output$AddStepsTimely <- renderPlot({
  
  BinPlot (input = input, question = "AddStepsTimely", title = "If your certifier requested additional steps to source organic seed, did they ask that you request seed in a timely manner?", xlab = XLabel(input, "Response"), ylab = "Percentage of Respondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Certifier Requests Contracting Organic Seed Production

```{r}
plotOutput("AddStepsContract")
```

```{r, context="server", AddStepsContract, echo=FALSE}
output$AddStepsContract <- renderPlot({
  
  BinPlot (input = input, question = "AddStepsContract", title = "If your certifier requested additional steps to source organic seed, did they ask that you contract organic seed production?", XLabel(input, "Response"), ylab = "Percentage of Respondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

Organic Seed Production {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================
  
### Producers Currently Saving Own Seed
  
```{r}
plotOutput("SeedSourceOwn0or100")
```

```{r, context="server", SeedSourceOwn0or100, echo=FALSE}
output$SeedSourceOwn0or100 <- renderPlot({
  
  BoxPlot (input = input, question = "SeedSourceOwn0or100", title = "Percentage of Producers Growing Their Own Seed", xlab = XLabel(input, "Share of producers"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### 2021 Regional Map of Producers Currently Saving Own Seed
  
```{r}
plotOutput("SeedSourceOwn0or100_2021Map")
```

```{r, context="server", SeedSourceOwn0or100_2021Map, echo=FALSE}
output$SeedSourceOwn0or100_2021Map <- renderPlot({
  if (input$Y2021 & input$state == "All") {
    
    GradientMap (input = input, question = "SeedSourceOwn0or100", title = "Percentage of 2021 Producers Growing Their Own Seed", catlab =  "Percentage", year = "2021")
    
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### 2016 Regional Map of Producers Currently Saving Own Seed
  
```{r}
plotOutput("SeedSourceOwn0or100_2016Map")
```

```{r, context="server", SeedSourceOwn0or100_2016Map, echo=FALSE}
output$SeedSourceOwn0or100_2016Map <- renderPlot({
  if (input$Y2016 & input$state == "All") {
    
    GradientMap (input = input, question = "SeedSourceOwn0or100", title = "Percentage of 2016 Producers Growing Their Own Seed", catlab =  "Percentage", year = "2016")
    
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### 2011 Regional Map of Producers Currently Saving Own Seed
  
```{r}
plotOutput("SeedSourceOwn0or100_2011Map")
```

```{r, context="server", SeedSourceOwn0or100_2011Map, echo=FALSE}
output$SeedSourceOwn0or100_2011Map <- renderPlot({
  if (input$Y2011 & input$state == "All") {
    
    GradientMap (input = input, question = "SeedSourceOwn0or100", title = "Percentage of 2011 Producers Growing Their Own Seed", catlab =  "Percentage", year = "2011")
    
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Current Seed Production Status

```{r}
plotOutput("ProduceOGSeed")
```

```{r, context="server", ProduceOGSeed, echo=FALSE}
output$ProduceOGSeed <- renderPlot({
  
  BinPlot (input = input, question = "ProduceOGSeed", title = "Which of the following categories best fit your situation pertaining to producing organic seed?", xlab = XLabel(input, "Interest level"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Interest in Growing Organic Seed

```{r}
plotOutput("SeedInterest")
```

```{r, context="server", SeedInterest, echo=FALSE}
output$SeedInterest <- renderPlot({
  
  BinPlot (input = input, question = "SeedInterest", title = "Are you interested in producing organic seed for commercial use at some point in the future?", xlab = XLabel(input, "Seed production category"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### 2021 Regional Map of Producers Interested in Growing Seed
  
```{r}
plotOutput("SeedInterestYN_2021Map")
```

```{r, context="server", SeedInterestYN_2021Map, echo=FALSE}
output$SeedInterestYN_2021Map <- renderPlot({
  if (input$Y2021 & input$state == "All") {
    
    GradientMap (input = input, question = "SeedInterestYN", title = "Percentage of 2021 Producers Interested in Growing Seed", catlab =  "Percentage", year = "2021")
    
  }
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

Factors in Not Purchasing Organic Seed {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================
  
### Lack of Seed Treatments
  
```{r}
plotOutput("NoOGSeedTreat")
```

```{r, context="server", NoOGSeedTreat, echo=FALSE}
output$NoOGSeedTreat <- renderPlot({
  
  BinPlot (input = input, question = "NoOGSeedTreat", title = "How much was lack of seed treatments (such as pelleting or priming) a factor in your decision NOT to purchase organic seed?", xlab = XLabel(input, "Factors"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Lack of Seed Treatments a Moderate or Significant Factor by Vegetable Acreage
  
```{r}
plotOutput("NoOGSeedTreatByVegAcre")
```

```{r, context="server", NoOGSeedTreatByVegAcre, echo=FALSE}
output$NoOGSeedTreatByVegAcre <- renderPlot({
  
CatPlot (input = input, category = "VegiAcreageBins", question = "NoOGSeedTreatModSig", title = "Lack of Seed Treatments a Moderate or Significant Factor by Vegetable Acreage", xlab = XLabel(input,"Vegetable acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Lack of Seed Treatments a Moderate or Significant Factor by Field Crop Acreage
  
```{r}
plotOutput("NoOGSeedTreatByFieldAcre")
```

```{r, context="server", NoOGSeedTreatByFieldAcre, echo=FALSE}
output$NoOGSeedTreatByFieldAcre <- renderPlot({
  
CatPlot (input = input, category = "FieldAcreageBins", question = "NoOGSeedTreatModSig", title = "Lack of Seed Treatments a Moderate or Significant Factor by Field Crop Acreage", xlab = XLabel(input,"Field crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Lack of Seed Treatments a Moderate or Significant Factor by Forage Crop Acreage
  
```{r}
plotOutput("NoOGSeedTreatByForageAcre")
```

```{r, context="server", NoOGSeedTreatByForageAcre, echo=FALSE}
output$NoOGSeedTreatByForageAcre <- renderPlot({
  
CatPlot (input = input, category = "ForageAcreageBins", question = "NoOGSeedTreatModSig", title = "Lack of Seed Treatments a Moderate or Significant Factor by Forage Crop Acreage", xlab = XLabel(input,"Forage crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Buyer Requires Variety Not Available As Organic

```{r}
plotOutput("NoOGSeedProcessor")
```

```{r, context="server", NoOGSeedProcessor, echo=FALSE}
output$NoOGSeedProcessor <- renderPlot({
  
  BinPlot (input = input, question = "NoOGSeedProcessor", title = "How much was processor (buyer) requiring or supplying varieties that are not available organically a factor in your decision NOT to purchase organic seed?", xlab = XLabel(input, "Factors"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Buyer Requires Variety Not Available As Organic by Vegetable Acreage
  
```{r}
plotOutput("NoOGSeedProcessorByVegAcre")
```

```{r, context="server", NoOGSeedProcessorByVegAcre, echo=FALSE}
output$NoOGSeedProcessorByVegAcre <- renderPlot({
  
CatPlot (input = input, category = "VegiAcreageBins", question = "NoOGSeedProcessorModSig", title = "Buyer Requires Variety Not Available As Organic by Vegetable Acreage", xlab = XLabel(input,"Vegetable acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Buyer Requires Variety Not Available As Organic by Field Crop Acreage
  
```{r}
plotOutput("NoOGSeedProcessorByFieldAcre")
```

```{r, context="server", NoOGSeedProcessorByFieldAcre, echo=FALSE}
output$NoOGSeedProcessorByFieldAcre <- renderPlot({
  
CatPlot (input = input, category = "FieldAcreageBins", question = "NoOGSeedProcessorModSig", title = "Buyer Requires Variety Not Available As Organic by Field Crop Acreage", xlab = XLabel(input,"Field crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Buyer Requires Variety Not Available As Organic by Forage Crop Acreage
  
```{r}
plotOutput("NoOGSeedProcessorByForageAcre")
```

```{r, context="server", NoOGSeedProcessorByForageAcre, echo=FALSE}
output$NoOGSeedProcessorByForageAcre <- renderPlot({
  
CatPlot (input = input, category = "ForageAcreageBins", question = "NoOGSeedProcessorModSig", title = "Buyer Requires Variety Not Available As Organic by Forage Crop Acreage", xlab = XLabel(input,"Forage crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Insufficient Quantity of Seed

```{r}
plotOutput("NoOGSeedQuant")
```

```{r, context="server", NoOGSeedQuant, echo=FALSE}
output$NoOGSeedQuant <- renderPlot({
  
  BinPlot (input = input, question = "NoOGSeedQuant", title = "How much was an insufficient quantity of seed a factor in your decision NOT to purchase organic seed?", xlab = XLabel(input, "Factors"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Insufficient Quantity of Seed by Vegetable Acreage
  
```{r}
plotOutput("NoOGSeedQuantByVegAcre")
```

```{r, context="server", NoOGSeedQuantByVegAcre, echo=FALSE}
output$NoOGSeedQuantByVegAcre <- renderPlot({
  
CatPlot (input = input, category = "VegiAcreageBins", question = "NoOGSeedQuantModSig", title = "Insufficient Quantity of Seed by Vegetable Acreage", xlab = XLabel(input,"Vegetable acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Insufficient Quantity of Seed by Field Crop Acreage
  
```{r}
plotOutput("NoOGSeedQuantByFieldAcre")
```

```{r, context="server", NoOGSeedQuantByFieldAcre, echo=FALSE}
output$NoOGSeedQuantByFieldAcre <- renderPlot({
  
CatPlot (input = input, category = "FieldAcreageBins", question = "NoOGSeedQuantModSig", title = "Insufficient Quantity of Seed by Field Crop Acreage", xlab = XLabel(input,"Field crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Insufficient Quantity of Seed by Forage Crop Acreage
  
```{r}
plotOutput("NoOGSeedQuantByForageAcre")
```

```{r, context="server", NoOGSeedQuantByForageAcre, echo=FALSE}
output$NoOGSeedQuantByForageAcre <- renderPlot({
  
CatPlot (input = input, category = "ForageAcreageBins", question = "NoOGSeedQuantModSig", title = "Insufficient Quantity of Seed by Forage Crop Acreage", xlab = XLabel(input,"Forage crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Save Own Seed

```{r}
plotOutput("NoOGSeedSave")
```

```{r, context="server", NoOGSeedSave, echo=FALSE}
output$NoOGSeedSave <- renderPlot({
  
  BinPlot (input = input, question = "NoOGSeedSave", title = "How much was saving your own seed a factor in your decision NOT to purchase organic seed?", xlab = XLabel(input, "Factors"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Save Own Seed by Vegetable Acreage
  
```{r}
plotOutput("NoOGSeedSaveByVegAcre")
```

```{r, context="server", NoOGSeedSaveByVegAcre, echo=FALSE}
output$NoOGSeedSaveByVegAcre <- renderPlot({
  
CatPlot (input = input, category = "VegiAcreageBins", question = "NoOGSeedSaveModSig", title = "Save Own Seed by Vegetable Acreage", xlab = XLabel(input,"Vegetable acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Save Own Seed by Field Crop Acreage
  
```{r}
plotOutput("NoOGSeedSaveByFieldAcre")
```

```{r, context="server", NoOGSeedSaveByFieldAcre, echo=FALSE}
output$NoOGSeedSaveByFieldAcre <- renderPlot({
  
CatPlot (input = input, category = "FieldAcreageBins", question = "NoOGSeedSaveModSig", title = "Save Own Seed by Field Crop Acreage", xlab = XLabel(input,"Field crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Save Own Seed by Forage Crop Acreage
  
```{r}
plotOutput("NoOGSeedSaveByForageAcre")
```

```{r, context="server", NoOGSeedSaveByForageAcre, echo=FALSE}
output$NoOGSeedSaveByForageAcre <- renderPlot({
  
CatPlot (input = input, category = "ForageAcreageBins", question = "NoOGSeedSaveModSig", title = "Save Own Seed by Forage Crop Acreage", xlab = XLabel(input,"Forage crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Distrust of organic seed quality

```{r}
plotOutput("NoOGSeedQual")
```

```{r, context="server", NoOGSeedQual, echo=FALSE}
output$NoOGSeedQual <- renderPlot({
  
  BinPlot (input = input, question = "NoOGSeedQual", title = "How much was distrust of organic seed quality a factor in your decision NOT to purchase organic seed?", xlab = XLabel(input, "Factors"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Distrust of organic seed quality by vegetable acreage
  
```{r}
plotOutput("NoOGSeedQualByVegAcre")
```

```{r, context="server",NoOGSeedQualByVegAcre, echo=FALSE}
output$NoOGSeedQualByVegAcre <- renderPlot({
  
CatPlot (input = input, category = "VegiAcreageBins", question = "NoOGSeedQualModSig", title = "Distrust of organic seed quality by Vegetable Acreage", xlab = XLabel(input,"Vegetable acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Distrust of organic seed quality by field crop acreage
  
```{r}
plotOutput("NoOGSeedQualByFieldAcre")
```

```{r, context="server",NoOGSeedQualByFieldAcre, echo=FALSE}
output$NoOGSeedQualByFieldAcre <- renderPlot({
  
CatPlot (input = input, category = "FieldAcreageBins", question = "NoOGSeedQualModSig", title = "Distrust of organic seed quality by field crop acreage", xlab = XLabel(input,"Field crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Distrust of organic seed quality by forage crop acreage
  
```{r}
plotOutput("NoOGSeedQualByForageAcre")
```

```{r, context="server",NoOGSeedQualByForageAcre, echo=FALSE}
output$NoOGSeedQualByForageAcre <- renderPlot({
  
CatPlot (input = input, category = "ForageAcreageBins", question = "NoOGSeedQualModSig", title = "Distrust of organic seed quality by forage crop acreage", xlab = XLabel(input,"Forage crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Price

```{r}
plotOutput("NoOGSeedPrice")
```

```{r, context="server", NoOGSeedPrice, echo=FALSE}
output$NoOGSeedPrice <- renderPlot({
  
  BinPlot (input = input, question = "NoOGSeedPrice", title = "How much was price a factor in your decision NOT to purchase organic seed?", xlab = XLabel(input, "Factors"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Price by Vegetable Acreage
  
```{r}
plotOutput("NoOGSeedPriceModSig")
```

```{r, context="server", NoOGSeedPriceModSig, echo=FALSE}
output$NoOGSeedPriceModSig <- renderPlot({
  
CatPlot (input = input, category = "VegiAcreageBins", question = "NoOGSeedPriceModSig", title = "Price by Vegetable Acreage", xlab = XLabel(input,"Vegetable acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Price by Field Crop Acreage
  
```{r}
plotOutput("NoOGSeedPriceByFieldAcre")
```

```{r, context="server", NoOGSeedPriceByFieldAcre, echo=FALSE}
output$NoOGSeedPriceByFieldAcre <- renderPlot({
  
CatPlot (input = input, category = "FieldAcreageBins", question = "NoOGSeedPriceModSig", title = "Price by Field Crop Acreage", xlab = XLabel(input,"Field crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Price by Forage Crop Acreage
  
```{r}
plotOutput("NoOGSeedPriceByForageAcre")
```

```{r, context="server", NoOGSeedPriceByForageAcre, echo=FALSE}
output$NoOGSeedPriceByForageAcre <- renderPlot({
  
CatPlot (input = input, category = "ForageAcreageBins", question = "NoOGSeedPriceModSig", title = "Price by Forage Crop Acreage", xlab = XLabel(input,"Forage crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Variety not available as organic seed

```{r}
plotOutput("NoOGSeedVar")
```

```{r, context="server", NoOGSeedVar, echo=FALSE}
output$NoOGSeedVar <- renderPlot({
  
  BinPlot (input = input, question = "NoOGSeedVar", title = "How much was the inavailability of specific varieties in organic seed a factor in your decision NOT to purchase organic seed?", xlab = XLabel(input, "Factors"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Variety not available as organic seed by Vegetable Acreage
  
```{r}
plotOutput("NoOGSeedVarByVegAcre")
```

```{r, context="server", NoOGSeedVarByVegAcre, echo=FALSE}
output$NoOGSeedVarByVegAcre <- renderPlot({
  
CatPlot (input = input, category = "VegiAcreageBins", question = "NoOGSeedVarModSig", title = "Variety not available as organic seed by Vegetable Acreage", xlab = XLabel(input,"Vegetable acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Variety not available as organic seed by Field Crop Acreage
  
```{r}
plotOutput("NoOGSeedVarByFieldAcre")
```

```{r, context="server", NoOGSeedVarByFieldAcre, echo=FALSE}
output$NoOGSeedVarByFieldAcre <- renderPlot({
  
CatPlot (input = input, category = "FieldAcreageBins", question = "NoOGSeedVarModSig", title = "Variety not available as organic seed by Field Crop Acreage", xlab = XLabel(input,"Field crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Variety not available as organic seed by Forage Crop Acreage
  
```{r}
plotOutput("NoOGSeedVarByForageAcre")
```

```{r, context="server", NoOGSeedVarByForageAcre, echo=FALSE}
output$NoOGSeedVarByVegAcre <- renderPlot({
  
CatPlot (input = input, category = "ForageAcreageBins", question = "NoOGSeedVarModSig", title = "Variety not available as organic seed by Forage Crop Acreage", xlab = XLabel(input,"Forage crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Lack of desirable genetic traits

```{r}
plotOutput("NoOGSeedTrait")
```

```{r, context="server", NoOGSeedTrait, echo=FALSE}
output$NoOGSeedTrait <- renderPlot({
  
  BinPlot (input = input, question = "NoOGSeedTrait", title = "How much was the lack of desirable genetic traits a factor in your decision NOT to purchase organic seed?", xlab = XLabel(input, "Factors"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Lack of desirable genetic traits by Vegetable Acreage
  
```{r}
plotOutput("NoOGSeedTraitByVegAcre")
```

```{r, context="server", NoOGSeedTraitByVegAcre, echo=FALSE}
output$NoOGSeedTraitByVegAcre <- renderPlot({
  
CatPlot (input = input, category = "VegiAcreageBins", question = "NoOGSeedTraitModSig", title = "Lack of desirable genetic traits by Vegetable Acreage", xlab = XLabel(input,"Vegetable acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Lack of desirable genetic traits by Field Crop Acreage
  
```{r}
plotOutput("NoOGSeedTraitByFieldAcre")
```

```{r, context="server", NoOGSeedTraitByFieldAcre, echo=FALSE}
output$NoOGSeedTraitByFieldAcre <- renderPlot({
  
CatPlot (input = input, category = "FieldAcreageBins", question = "NoOGSeedTraitModSig", title = "Lack of desirable genetic traits by Field Crop Acreage", xlab = XLabel(input,"Field crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

### Lack of desirable genetic traits by Forage Crop Acreage
  
```{r}
plotOutput("NoOGSeedTraitByForageAcre")
```

```{r, context="server", NoOGSeedTraitByForageAcre, echo=FALSE}
output$NoOGSeedTraitByForageAcre <- renderPlot({
  
CatPlot (input = input, category = "ForageAcreageBins", question = "NoOGSeedTraitModSig", title = "Lack of desirable genetic traits by Forage Crop Acreage", xlab = XLabel(input,"Forage crop acreage"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)
```

Opinions on Genetic Engineering and Organic Seeds {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================
  
### Company Testing for GE Contamination
  
```{r}
plotOutput("GMOTesting")
```

```{r, context="server", GMOTesting, echo=FALSE}
output$GMOTesting <- renderPlot({
  
  BinPlot (input = input, question = "GMOTesting", title = "Seed companies should conduct testing and report rates of GE (GMO) crop contamination in organic and conventional seed", xlab = XLabel(input, "Sentiment"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Federal GE Crop Regulations.

```{r}
plotOutput("Regulations")
```

```{r, context="server", Regulations, echo=FALSE}
output$Regulations <- renderPlot({
  
  BinPlot (input = input, question = "Regulations", title = "The federal regulations that oversee GE crop (GMOs) approvals are adequate for protecting my organic farm product(s) from potential contamination by GE crops (GMOs)", xlab = XLabel(input, "Sentiment"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### GE Risk For Organic

```{r}
plotOutput("RiskfromGMO")
```

```{r, context="server", RiskfromGMO, echo=FALSE}
output$RiskfromGMO <- renderPlot({
  
  BinPlot (input = input, question = "RiskfromGMO", title = "Unintentionally planting GE-contaminated seed on my farm puts at risk the integrity of my organic products", xlab = XLabel(input, "Sentiment"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Organic Seed for Organic Integrity

```{r}
plotOutput("OGSeedOGIntegrity")
```

```{r, context="server", OGSeedOGIntegrity, echo=FALSE}
output$OGSeedOGIntegrity <- renderPlot({
  
  BinPlot (input = input, question = "OGSeedOGIntegrity", title = "Organic seed is important to the integrity of organic food production", xlab = XLabel(input, "Sentiment"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Organic Breeding for Success of Organic Farming

```{r}
plotOutput("OGVarietiesSuccess")
```

```{r, context="server", OGVarietiesSuccess, echo=FALSE}
output$OGVarietiesSuccess <- renderPlot({
  
  BinPlot (input = input, question = "OGVarietiesSuccess", title = "Varieties bred for organic production are important to the overall success of organic agriculture", xlab = XLabel(input, "Sentiment"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

Organic Breeding Needs {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================
  
### Are There Crops in Need of Organic Plant Breeding 
  
```{r}
plotOutput("CropsNeedBreed")
```

```{r, context="server", CropsNeedBreed, echo=FALSE}
output$CropsNeedBreed <- renderPlot({
  
  BinPlot (input = input, question = "CropsNeedBreed", title = "Do you think there are crops in need of organic plant breeding?", xlab = XLabel(input, "Response"), ylab = "Percentage of Respondents")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

### Top 10 Crops in Need of Organic Breeding

```{r}
plotOutput("BreedTop10")
```

```{r, context="server", BreedTop10, echo=FALSE}
output$BreedTop10 <- renderPlot({
  
  BreedPlot (input = input, question = "BreedTop10", title = "Top 10 crops in most need of improvement", xlab = XLabel(input, "Crop"), ylab = "Percentage")
  
})  %>% bindCache(input$state, input$Y2021, input$Y2016, input$Y2011, input$crop_type, input$show_n, input$color_palette, input$crop_size, input$show_title)

```

Additional Figures {.storyboard data-navmenu="Crop producers"  data-width=700}
=====================================
  
### Average percent acreage planted to organic seed by crop type

```{r}
plotOutput("OGSeedByCrop")
```


```{r, context="server", OGSeedByCrop, echo=FALSE}
output$OGSeedByCrop <- renderPlot({
  
  CannedPlot (input = input, dataset = "ogbycrop", question = "PercentAcres", category = "CropType", title = "Average percent acreage planted to organic seed", xlab = "Crop type", ylab = "Average percent organic seed used")
  
})  %>% bindCache(input$Y2021, input$Y2016, input$Y2011, input$color_palette, input$show_title)

```

### Average percent acreage planted to organic seed by crop type

```{r}
plotOutput("totalogacres")
```


```{r, context="server", totalogacres, echo=FALSE}
output$totalogacres <- renderPlot({
  
  CannedPlot (input = input, dataset = "totalogacres", question = "PercentAcres", category = "CropType", title = "Percent of total acreage planted to organic seed", xlab = "Crop type", ylab = "Percent of total acreage")
  
})  %>% bindCache(input$Y2021, input$Y2016, input$Y2011, input$color_palette, input$show_title)

```

<!----
Data collection {.storyboard data-navmenu="Seed producers" data-width=700}
=======================================================================

### Data collection methods
  
We conducted a formal survey of organic seed growers and organic seed suppliers. The purpose was to identify the operational characteristics of producers and companies in the organic seed industry, assess the challenges they experience, and their perceptions on key issues facing organic seed. 
 
The survey was distributed to 416 seed producers from the National Organic Program list and 90 organic seed companies. We heard from 88 seed producers and 39 companies that range in scale and size. Together there were 127 responses out of 506 seed producers and companies, for a 25% response rate.

Those who have completed this survey take part in a number of organic seed-related activities:

* Breeding: 58 respondents  
* Seed production: 119 respondents  
* Seed handling and/or processing: 36 respondents  
* Seed retail: 67 respondents  

While respondents take part in a whole mix of activities, we provided a filter (left) to analyze the groups based on those that only take part in breeding and production ("Seed breeding & production only"), which is 54 respondents, and those that take part in some kind of seed handling and retail ("Seed production & retail"), which is 73 respondents.  

--->

Seed producer demographics {.storyboard data-navmenu="Seed producers" data-width=700}
=======================================================================

### Seed producer locations by region

```{r map prerender}
plotlyOutput("ProducerMap")
```

```{r map, context = "server"}
counts <- us_states %>% select(Region, regional_n) %>% unique() %>% arrange(regional_n)

us_states$n <- factor(us_states$regional_n)
levels(us_states$n) <- c(paste(counts[1,1], counts[1,2], sep = ": "),
                         paste(counts[2,1], counts[2,2], sep = ": "),
                         paste(counts[3,1], counts[3,2], sep = ": "),
                         paste(counts[4,1], counts[4,2], sep = ": "))

output$ProducerMap <- renderPlotly({
  mapPlot(input = input)
}) 

```

### What crops has your operation produced over the last five years?

```{r crop categort prerender}
plotlyOutput("CropCat")
``` 

```{r crop category, context = "server"}
output$CropCat <- renderPlotly({
  cropPlot(input = input)
}) 
```

### What was your operation's approximate gross annual revenue in 2019?

```{r income prerender}
plotlyOutput("ProducerIncome")
``` 

```{r income, context = "server"}
output$ProducerIncome <- renderPlotly({
  incomePlot(input = input)
}) 
```

### How many years have you been involved in farming and seed production?  

```{r years prerender}
plotlyOutput("ProducerYears")
``` 

```{r, context = "server"}
output$ProducerYears <- renderPlotly({
  yrsPlot(input = input)
}) 
```

Challenges {.storyboard data-navmenu="Seed producers" data-width=700}
=======================================================================

### Production challenges: How much have the following been a challenge to you in your work with organic seed?  

```{r prod challenges prerender}
plotlyOutput("ProductionChall")
``` 

```{r rendering prod challenges, context = "server"}
output$ProductionChall <- renderPlotly({
  challPlot(input = input, production = T)
})
```

### Non-production challenges: How much have the following been a challenge to you in your work with organic seed?  
```{r nonprod challenges prerender}
plotlyOutput("NonproductionChall")
``` 

```{r rendering nonprod challenges, context = "server"}
output$NonproductionChall <- renderPlotly({
  challPlot(input = input, production = F)
})
```

Seed producer perspectives {.storyboard data-navmenu="Seed producers" data-width=700}
=======================================================================

### For the following types of intellectual property protections, how would you describe their impact on the  organic seed system? 
```{r ipr prerender}
plotlyOutput("Produceripr")
``` 

```{r rendering ipr, context = "server"}
output$Produceripr <- renderPlotly({
  iprPlot(input = input)
})
```

### In your region, what do you think the effect of climate change will be on agriculture during your lifetime? 

```{r cceff prerender}
plotlyOutput("ProducerCCeff")
``` 

```{r rendering CCeff, context = "server"}
output$ProducerCCeff <- renderPlotly({
  cceffPlot(input = input)
})
```


<!----Researcher data collection {.storyboard data-navmenu="Researchers" data-width=700}
=======================================================================
### Overview

We conducted a formal survey of organic seed researchers. The purpose was to better understand the successes, challenges, and opportunities for organic seed research, as well as researchers' perspectives on key issues.  

The survey was distributed to a total of 77 researchers. Researchers were identified based on their receipt of organic research grants, participation in OSA research programs, recent publications on organic seed, and through a snowballing survey method. Of the 77 researchers contacted there were 51 full responses for a response rate of 66%. 
--->

Researcher demographics {.storyboard data-navmenu="Researchers" data-width=700}
=======================================================================

### Seed researcher locations by region

```{r map researcher prerender}
plotlyOutput("ResearcherMap")
```

```{r map researcher, context = "server"}
counts <- us_states_r %>% select(Region, regional_n) %>% unique() %>% arrange(regional_n)

us_states_r$n <- factor(us_states_r$regional_n)
levels(us_states_r$n) <- c(paste(counts[1,1], counts[1,2], sep = ": "),
                         paste(counts[2,1], counts[2,2], sep = ": "),
                         paste(counts[3,1], counts[3,2], sep = ": "),
                         paste(counts[4,1], counts[4,2], sep = ": "))

output$ResearcherMap <- renderPlotly({
  researchermapPlot(input = input)
}) 

```

### What crops do you work with in your research?

```{r crop category researcher prerender}
plotlyOutput("ResearcherCrop")
``` 

```{r crop category researcher, context = "server"}
output$ResearcherCrop <- renderPlotly({
  researchercropPlot(input = input)
}) 
```


### How much expertise do you consider yourself to have in each of the following topics?

```{r expertise prerender}
plotlyOutput("Expertise")
``` 

```{r expertise, context = "server"}
output$Expertise <- renderPlotly({
  expertisePlot(input = input)
})
```

### What best identifies your research area? 

```{r discipline prerender}
plotlyOutput("Discipline")
``` 

```{r discipline, context = "server"}
output$Discipline <- renderPlotly({
  disciplinePlot(input = input)
}) 
```


Project outcomes {.storyboard data-navmenu="Researchers" data-width=700}
=======================================================================

### What were the successes and/or outcomes from your most recent organic seed project?

```{r success prerender}
plotlyOutput("ResearcherSuccess")
``` 


```{r success, context = "server"}
output$ResearcherSuccess <- renderPlotly({
  successPlot(input = input)
})
```

### What were the challenges experienced in your most recent organic seed project?

```{r projchallenge prerender}
plotlyOutput("ResearcherChallenges")
``` 


```{r projchallenge, context = "server"}
output$ResearcherChallenges <- renderPlotly({
  projchallPlot(input = input)
})
```

### Were any finished varieties or breeding material released as part of this project?

```{r finished rendered}
plotlyOutput("Finished")
```

```{r finished, context = "server"}
output$Finished <- renderPlotly({
  finishedPlot(input = input)
})
```

### What mechanisms, if any, were used to protect released material? 
```{r protections rendered}
plotlyOutput("Mechanisms")
```

```{r protections, context = "server"}
output$Mechanisms <- renderPlotly({
  mechanismsPlot(input = input)
})
```

Researcher perspectives {.storyboard data-navmenu="Researchers" data-width=700}
=======================================================================

### For the following types of intellectual property protections, how would you describe their impact on the  organic seed system? 
```{r ipr researcher prerender}
plotlyOutput("Researcheripr")
``` 

```{r rendering researcher ipr, context = "server"}
output$Researcheripr <- renderPlotly({
  researcheriprPlot(input = input)
})
```

### In your region, what do you think the effect of climate change will be on agriculture during your lifetime? 

```{r cceff researcher prerender}
plotlyOutput("ResearcherCCeff")
``` 

```{r rendering researcher CCeff, context = "server"}
output$ResearcherCCeff <- renderPlotly({
  researchercceffPlot(input = input)
})
```

### How important are the following crop characteristics in the context of your research? 

```{r priority prerender}
plotlyOutput("ResearcherPriority")
``` 

```{r priority, context = "server"}
output$ResearcherPriority <- renderPlotly({
  priorityPlot(input = input)
})
```

<!--- Data collection methods {data-navmenu="Network" data-width=700}
=======================================================================

Column
--------------------------
### Data collection {data-height=300}

We surveyed 127 people in the seed supply chain (seed breeders, producers, handlers and retailers) between 2020-2021, 107 of whom shared information about their networks. These 107 people named 238 new actors for a total of 345 total actors in the network. These networks can be binned into three groups:  

* Information & education: Who stakeholders get information from and who they collaborate with in research projects  
* Supply chain: Who stakeholders have contracts with and buy, sell and rent from   
* Germplasm & seed movement: Who people get breeding material from and exchange seed with

Column
--------------------------
### Overview of networks {data-height=700}
Seeds systems are complex networks that involve a wide range of actors, from seed breeders and researchers, seed producers, handlers and retailers, as well as the organizations and agencies that support and regulate the seed value chain. Looking looking at the connections and composition of the organic seed network can help us understand whether or not the network is supporting a resilient seed system. Networks can be measured based on three key features:

* **Centralization:** Having a centralized networks means that a small group of actors are the go-to people (think about a hub with many spokes). This kind of network can be really great for diffusing information and efficiently allocating resources, but may reduce diversity and create potential vulnerability to the system if a central actor were to leave or be removed from the network.  

* **Cooperation:** When three actors are connected in a triangle, this indicates a "cooperative" relationship -- it is strong and there is trust and/or ability to monitor one another. The degree to which actors cluster together into triangles can help indicate the strength of cooperation in a network.  

* **Diversity:** Based on the composition of an actor's connections we can quantify an actor's network diversity on two fronts: 1) the diversity of connections they make to people from sectors different than theirs (e.g. a breeder reaching out to a public agency), and 2) the diversity of connections they make to people in geographic regions other than theirs. 

--->

Seed network {.storyboard} 
=======================================================================
<!---# data-navmenu="Network" data-width=700> 
--->

### Organic seed network visualization

```{r networkmap prerender}
plotOutput("Network")
```

```{r networkmap, context = "server"}
output$Network <- renderPlot({
  netPlot(input = input)})
```

<!---### Organic seed network map

```{r network prerender}
plotOutput("Networkmap")
```

```{r network, context = "server"}
output$Networkmap <- renderPlot({
  netmapPlot(input = input)})
```
--->
### Network descriptives

<!---##### Network-level measures {data-height=272}

```{r summary net prerender}
tableOutput("netsummary")
``` 

```{r rendering summary net, context = "server"}
output$netsummary <- renderTable({
  netDesc(input = input, summary.object = summary.net)})
```
--->

##### Actors  {data-height=348}
```{r summary role prerender}
tableOutput("rolesummary")
``` 

```{r rendering role, context = "server"}
output$rolesummary <- renderTable({
  netDesc(input = input, summary.object = roles)})
```

##### Regions {data-height=380}
```{r summary region prerender}
tableOutput("regionsummary")
``` 

```{r rendering location, context = "server"}
output$regionsummary <- renderTable({
  netDesc(input = input, summary.object = locations)})
```


